**Density Dependence**

### 2023-02-02 Rmd/mseMac.Rmd

```{r, pkgs}
library(FLCore)
library(FLBRP)
library(FLasher)
library(FLAssess)
library(FLife)
library(ggplotFL)

@@

```{r}
source("../R/dd.R")
```

```{r, dbox}
dropboxdir<-try(file.path(get_dropbox(), "dd"))

>>>>

```{r, pkgs}

library(FLCore)    # install.packages("FLCore", repos="http://flr-project.org/R")
library(FLBRP)     # install.packages("FLBRP", repos="http://flr-project.org/R")
library(FLasher)   # install.packages("FLasher", repos="http://flr-project.org/R")
library(FLAssess)  # install.packages("FLAssess", repos="http://flr-project.org/R")
library(FLife)     # install.packages("FLife", repos="http://flr-project.org/R")
library(ggplotFL)

@@

```{r}
source("../R/dd.R")
source("../R/get_dropbox.r")
```

```{r, dbox}
dropboxdir<-try(file.path(get_dropbox(), "pelagics"))
